---
title: |
  | \vspace{4cm} \LARGE{"WIP - Web Content Report"}
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook: default
---
```{r, include=FALSE}
# Open Data
load( file = "GA_VBC(5-6-18).RData")
load( file = "save_docs.RData")
#Load Dependencies
library(tinytex)
library(wordcloud)
library(topicmodels)
library(googleAnalyticsR)
library(dplyr)
library(httr)
library(extrafont)
library(RCurl)
library(XML)
library(foreach)
library(stringr)
library(ggplot2)
library(lubridate)
library(quanteda)
library(tm)

loadfonts()

#Read custom functions
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
toNothing <- content_transformer(function (x , pattern ) gsub(pattern, "", x))
simpleCap <- function(x) {
	s <- strsplit(x, " ")[[1]]
	if (!is.na(s[1])) {return(paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "", collapse = " "))} else {
		return(NA)}}
my_theme <- function(){theme_light() +theme(text = element_text(family = "Open Sans"),  
		plot.title = element_text(size = 12, color = "gray30"),   # Set up the title style
		plot.subtitle = element_text(size = 10, color = "black"), # Set up the subtitle style
		plot.margin = unit(c(.05,.05,.05,.05), "cm"),                 # Add white space at the top and left
		panel.grid = element_blank(),#panel.border = element_blank(),
		axis.title = element_blank(),axis.ticks = element_blank(),#axis.text.x = element_blank(),
		axis.text.y = element_text(size = 9, color = "gray10"))}
current_date=format(Sys.time(), "%Y-%m-%d")
current_date=ymd(current_date)

#name="Vanessa Brown Calder"
begin=min(df_final$obs_day)
end=max(df_final$obs_day)
name=df_final$author[1]
name=as.character(name)
name
```


```{r echo=FALSE, fig.align="center"}
doc=Corpus(VectorSource(save_docs))
doc <- tm_map(doc, removeNumbers)
doc <- tm_map(doc, tolower)
doc <- tm_map(doc, stripWhitespace)
doc <- tm_map(doc, removePunctuation)
doc <- tm_map(doc, PlainTextDocument)
doc <- tm_map(doc, toSpace, "/")
doc <- tm_map(doc, toSpace, "@")
doc <- tm_map(doc, toSpace, "\\|")
doc <- tm_map(doc, toNothing, "-")
doc <- tm_map(doc, toNothing, "—")
doc <- tm_map(doc, toNothing, "–")
doc <- tm_map(doc, removeWords, stopwords("english"))
doc <- tm_map(doc, removeWords, c("the", "can",'did','like', 'and', 'null', 'one'))
# creating of document matrix
tdm <- TermDocumentMatrix(doc)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
#head(d, 10)
set.seed(12)
wordcloud(words = d$word, freq = d$freq, min.freq = 3,max.words=150,random.order = FALSE,rot.per=.35,vfont=c("sans serif","plain"),colors=brewer.pal(8, "Dark2"))

```

This is `r (name)`'s web analytics report from between the dates `r (begin)` and `r (end)`.

\pagebreak

**Total unique viewers with top content on high traffic days highlighted**

Colored by topic between the dates `r (begin)` and `r (end)`.

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=9.5, fig.width=10}
# Line Chart
total_line =subset(df_final, type != "events"&type !="multimedia") # Remove events
total_line=aggregate(sessions ~ title + author_categories + obs_day, total_line, sum)
total_line$big_day <- ifelse(total_line$sessions > 500, paste0(total_line$title,"(",as.character(total_line$obs_day),")"), "")

line=total_line %>%
ggplot(aes(x=obs_day,y=sessions,group=author_categories,colour=author_categories))+geom_line()+
	theme(axis.text.x=element_text(angle=90,hjust = 1),legend.position="none")+my_theme()+
	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank())+
	scale_y_continuous(expand = c(0, .3))

library(ggrepel)
line + geom_label_repel(data = subset(total_line %>% group_by(title) %>% top_n(n=10, wt=big_day))
												    ,	aes(label=big_day), size=4)+ theme(legend.position = "None")   # label

```

\pagebreak

**Count of published content by `r (name)`, colored by co-authorship**

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
Bar_type_df =subset(df_final, type != "events") # Remove events
Bar_type_df$collaboration_yn=ifelse(Bar_type_df$author!=Bar_type_df$author_full & length(Bar_type_df$author_full)!=0, "Co-Authored", ifelse(Bar_type_df$author==Bar_type_df$author_full, "Sole Author",0))
Bar_type_df<-Bar_type_df %>% distinct(type,title,collaboration_yn,one)

ggplot(data=Bar_type_df,aes(x=type,y=one,fill=collaboration_yn))+
ggtitle(sprintf("Total Content: %s",sum(Bar_type_df$one)), 
subtitle=sprintf("",sum(Bar_type_df$one)))+
geom_bar(stat="identity", width=0.8)+ my_theme()+theme(legend.position="bottom", 
legend.box = "horizontal")+theme(legend.title=element_blank())+
	scale_y_continuous(expand = c(0, .3)) 

```

**Popular Co-Authors for `r (name)` (Multimedia Excluded)**

```{r, echo=FALSE, message=FALSE,warning = FALSE}
pie =subset(df_final, 
		  	type != "events"
		  & type != "multimedia"
		  )
pie$co_authors=trimws(pie$co_authors)
pie$collaboration_yn=ifelse(pie$author==pie$author_full, "Sole Author",
	ifelse(pie$author!=pie$author_full | !is.na(pie$co_authors), "Co-Authored",0))
pie=pie[(pie$collaboration_yn)=='Co-Authored',]
pie <- aggregate(one ~ co_authors, pie, sum)
pie$per = pie$one/sum(pie$one)
pie$label <- scales::percent(pie$per)
pie_chart=ggplot(pie, aes(x = '', y=per, fill=(co_authors)) ) +
	geom_bar(width = 1,stat="identity")+coord_polar("y",start=0) +
	labs(fill='co-authors') + xlab("") + ylab("")+  geom_text(aes(x=1, label=label), 
	position = position_stack(vjust = .5))+ theme_void()
pie_chart
```
\pagebreak


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=12, fig.width=10}
### Generate time period dates ###
thirty_days= subset(df_final , days_aft_pub <= 30)
thirty_days$days_aft_pub= ifelse(thirty_days$days_aft_pub < 0, 0, thirty_days$days_aft_pub)
thirty_days =subset(thirty_days, type == "blog") # blogs only
thirty_days=aggregate(sessions ~ title+author_categories, thirty_days, sum)
thirty_days$title<-factor(thirty_days$title,levels=thirty_days$title[order(thirty_days$sessions)])

ggplot(data=thirty_days, aes(x=title,y=sessions,colour=author_categories) ) +
	ggtitle(sprintf("Blog performance within 30 Days of Publication", name))+ #,subtitle = "Unique User Views" ) +
	geom_bar(aes(fill = author_categories),stat="identity",width=.5, position = "dodge")+coord_flip()+my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) +
	scale_y_continuous(expand = c(0, .3))
```

\pagebreak

**Top performing content within first 45 Days of Publication**

Unique User Visits

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=7, fig.width=8}
### Generate time period dates ###
ninty_days =subset(df_final, days_aft_pub <= 50 & type != "events") # no events
ninty_days$days_aft_pub= ifelse(ninty_days$days_aft_pub < 0, 0, ninty_days$days_aft_pub)
ninty_days=aggregate(sessions ~ title+author_categories+type, ninty_days, sum)
ninty_days<-filter(ninty_days, row_number(-sessions) <= 20)

ninty_days$cat_type= paste0(ninty_days$author_categories," (",ninty_days$type,")")

ninty_days$title<-factor(ninty_days$title,levels=ninty_days$title[order(ninty_days$sessions)])

ggplot(data=ninty_days, aes(x=title,y=sessions,colour=cat_type) ) +
	#ggtitle(sprintf("Content performance within first 45 Days of Publication", name), subtitle = "Unique User Visits" ) +
	geom_bar(aes(fill = cat_type),stat="identity",width=.4, position = "dodge")+coord_flip()+my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) +
	scale_y_continuous(expand = c(.01, .3))
```

\pagebreak
Multimedia content (e.g. Podcasts) has a noticeably lower exit rate.  A likely explanation for why this is the case has to with the fact that links to other Cato web-content are prominently displayed for media.  This insight strongly suggests that links to related content ought to be similarly placed in other forms content (blogs, commentary, policy analyses, etc.)

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=9, fig.width=8.5}
### Generate time period dates ###
exit_rate =subset(df_final,  type != "events") # no events
exit_rate$days_aft_pub= ifelse(exit_rate$days_aft_pub < 0, 0, exit_rate$days_aft_pub)
exit_rate$cat_type= paste0(exit_rate$author_categories," (",exit_rate$type,")")
exit_rate$web_recs=ifelse(exit_rate$type=="blog"|exit_rate$type=="commentary"|exit_rate$type=="policy analysis"|exit_rate$type=="tax budget bulletin", "No","Yes")

exit_rate1=aggregate(exitRate ~ cat_type+web_recs, exit_rate, mean)
exit_rate1$cat_type<-factor(exit_rate1$cat_type,levels=exit_rate1$cat_type[order(exit_rate1$exitRate)])
bar = ggplot(data=exit_rate1, aes(x=cat_type,y=exitRate,colour=web_recs) ) +
	ggtitle(sprintf("Average Exit Rate", name), subtitle = "" ) +
	geom_bar(aes(fill = web_recs),stat="identity",width=.4, position = "dodge")+my_theme() +
	geom_label_repel(data = exit_rate1,	aes(label=exitRate), size=4.5,show_guide=F)+ theme(legend.position = "None")+coord_flip()+
	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank()) +
	scale_y_continuous(expand = c(.01, .3))#+axis.text.x=element_blank()
bar

```
\pagebreak

This section examines time spent on reading an article relative to the number of words of text in the article.  Below are the 10 best and worst performing articles.  Multimedia (e.g. Podcasts) are ignored. This measure is designed to give you a rough idea of the types of articles people are likely to read through. 

**Note:** This measure has some methodological issues related to sample size that need to be addressed and thus should be treated solely as an illustration.  

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
#Time per Article
Audience_Captivation =subset(df_final, type != "events" & type != "multimedia") # Remove Events and Multimedia
Audience_Captivation <- aggregate(avg_MinPerWord ~ title+author_categories, Audience_Captivation, mean)

# Happy
Happy_audience=filter(Audience_Captivation, row_number(-avg_MinPerWord) <= 10)
Happy_audience <- Happy_audience %>% arrange(avg_MinPerWord)
Happy_audience$title<-factor(Happy_audience$title,levels=Happy_audience$title[order(Happy_audience$avg_MinPerWord)])
ggplot(data=Happy_audience, aes(x=title, y=avg_MinPerWord, fill=author_categories) ) +
	ggtitle(sprintf("10 Best Audience Attrition", name),subtitle = "Time Spent per Word in Aticle Text" ) +
	geom_bar(stat="identity", width=0.5)+ coord_flip() + my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) 
```

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
# Sad Audience
sad_audience<-filter(Audience_Captivation, row_number(avg_MinPerWord) <= 10)
sad_audience <- sad_audience %>% arrange(avg_MinPerWord)
sad_audience$title<-factor(sad_audience$title,levels=sad_audience$title[order(sad_audience$avg_MinPerWord)])
ggplot(data=sad_audience, aes(x=title, y=avg_MinPerWord, fill=author_categories))+
	ggtitle(sprintf("10 Worst Audience Attrition", name),subtitle="Time Spent per Word in Aticle Text")+
	geom_bar(stat="identity", width=0.5)+ coord_flip() + my_theme()+
	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank())

```

More to come on this...
