---
title: |
  | \vspace{4cm} \LARGE{"WIP - Web Content Report"}
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_notebook: default
---
```{r, include=FALSE}
# Open Data
load( file = "GA_VBC(5-6-18).RData")
load( file = "save_docs.RData")
#Load Dependencies
library(tinytex)
library(wordcloud)
library(topicmodels)
library(googleAnalyticsR)
library(dplyr)
library(httr)
library(extrafont)
library(RCurl)
library(XML)
library(foreach)
library(stringr)
library(ggplot2)
library(lubridate)
library(quanteda)
library(tm)

loadfonts()

#Read custom functions
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
toNothing <- content_transformer(function (x , pattern ) gsub(pattern, "", x))
simpleCap <- function(x) {
	s <- strsplit(x, " ")[[1]]
	if (!is.na(s[1])) {return(paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "", collapse = " "))} else {
		return(NA)}}
my_theme <- function(){theme_light() +theme(text = element_text(family = "Open Sans"),  
		plot.title = element_text(size = 12, color = "gray30"),   # Set up the title style
		plot.subtitle = element_text(size = 10, color = "black"), # Set up the subtitle style
		plot.margin = unit(c(.05,.05,.05,.05), "cm"),                 # Add white space at the top and left
		panel.grid = element_blank(),#panel.border = element_blank(),
		axis.title = element_blank(),axis.ticks = element_blank(),#axis.text.x = element_blank(),
		axis.text.y = element_text(size = 9, color = "gray10"))}
current_date=format(Sys.time(), "%Y-%m-%d")
current_date=ymd(current_date)

#name="Vanessa Brown Calder"
begin=min(df_final$obs_day)
end=max(df_final$obs_day)
name=df_final$author[1]
name=as.character(name)
name
```


```{r echo=FALSE, fig.align="center"}
doc=Corpus(VectorSource(save_docs))
doc <- tm_map(doc, removeNumbers)
doc <- tm_map(doc, tolower)
doc <- tm_map(doc, stripWhitespace)
doc <- tm_map(doc, removePunctuation)
doc <- tm_map(doc, PlainTextDocument)
doc <- tm_map(doc, toSpace, "/")
doc <- tm_map(doc, toSpace, "@")
doc <- tm_map(doc, toSpace, "\\|")
doc <- tm_map(doc, toNothing, "-")
doc <- tm_map(doc, toNothing, "—")
doc <- tm_map(doc, toNothing, "–")
doc <- tm_map(doc, removeWords, stopwords("english"))
doc <- tm_map(doc, removeWords, c("the", "can",'did','like', 'and', 'null', 'one'))
# creating of document matrix
tdm <- TermDocumentMatrix(doc)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
#head(d, 10)
set.seed(12)
wordcloud(words = d$word, freq = d$freq, min.freq = 3,max.words=150,random.order = FALSE,rot.per=.35,vfont=c("sans serif","plain"),colors=brewer.pal(8, "Dark2"))

```

This is `r (name)`'s web analytics report from between the dates `r (begin)` and `r (end)`.

\pagebreak

Below is a count of content published by `r (name)` that has been colored according to co-authorship.

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
Bar_type_df =subset(df_final, type != "events") # Remove events
Bar_type_df$collaboration_yn=ifelse(Bar_type_df$author!=Bar_type_df$author_full & length(Bar_type_df$author_full)!=0, "Co-Authored", ifelse(Bar_type_df$author==Bar_type_df$author_full, "Sole Author",0))

Bar_type_df<-Bar_type_df %>% distinct(type,title,collaboration_yn,one)
title_name=sprintf("%s's Content Breakdown",name)

ggplot(data=Bar_type_df,aes(x=type,y=one,fill=collaboration_yn))+
ggtitle(sprintf("%s's Content Breakdown ", name), # Add the title and subtitle
subtitle=sprintf("\n Total Content: %s",sum(Bar_type_df$one)))+
geom_bar(stat="identity", width=0.8)+ my_theme()+theme(legend.position="bottom", 
legend.box = "horizontal")+theme(legend.title=element_blank())+
	scale_y_continuous(expand = c(0, .3)) #+ scale_x_continuous(expand = c(0, 0))

```


**Total unique viewers with 10 top content on that**
colored by topic between the dates `r (begin)` and `r (end)`.

```{r, echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
# Line Chart
total_line =subset(df_final, type != "events"&type !="multimedia") # Remove events
total_line=aggregate(sessions ~ title + author_categories + obs_day, total_line, sum)
total_line$big_day <- ifelse(total_line$sessions > 500, paste(total_line$title," (",total_line$obs_day,")"), "")

line=total_line %>%
ggplot(aes(x=obs_day,y=sessions,group=author_categories,colour=author_categories))+geom_line()+
	theme(axis.text.x=element_text(angle=90,hjust = 1),legend.position="none")+my_theme()+
	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank())+
	scale_y_continuous(expand = c(0, .3))

library(ggrepel)
line + geom_label_repel(data = subset(total_line %>% group_by(title) %>% #summarise(sessions = max(sessions)) %>% #  tapply(total_line$sessions, total_line$title, max) %>% 
												    top_n(n=10, wt=big_day))
												    ,	aes(label=big_day), size=4.5)+ theme(legend.position = "None")   # label


```


\pagebreak

**Popular Co-Authors for `r (name)`**

Note: multimedia is ommitted.

```{r, echo=FALSE, message=FALSE,warning = FALSE}
pie =subset(df_final, 
		  	type != "events"
		  & type != "multimedia"
		  )
pie$co_authors=trimws(pie$co_authors)
pie$collaboration_yn=ifelse(pie$author==pie$author_full, "Sole Author",
	ifelse(pie$author!=pie$author_full | !is.na(pie$co_authors), "Co-Authored",0))
pie=pie[(pie$collaboration_yn)=='Co-Authored',]
pie <- aggregate(one ~ co_authors, pie, sum)
pie$per = pie$one/sum(pie$one)
pie$label <- scales::percent(pie$per)
pie_chart=ggplot(pie, aes(x = '', y=per, fill=(co_authors)) ) +
	geom_bar(width = 1,stat="identity")+coord_polar("y",start=0) +
	labs(fill='co-authors') + xlab("") + ylab("")+  geom_text(aes(x=1, label=label), 
	position = position_stack(vjust = .5))+ theme_void() + ggtitle(sprintf("%s's co-authors", name))
pie_chart
```

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=6}
### Generate time period dates ###
thirty_days= subset(df_final , days_aft_pub <= 30)
thirty_days$days_aft_pub= ifelse(thirty_days$days_aft_pub < 0, 0, thirty_days$days_aft_pub)
thirty_days =subset(thirty_days, type == "blog") # blogs only
thirty_days=aggregate(sessions ~ title+author_categories, thirty_days, sum)
thirty_days$title<-factor(thirty_days$title,levels=thirty_days$title[order(thirty_days$sessions)])

ggplot(data=thirty_days, aes(x=title,y=sessions,colour=author_categories) ) +
	ggtitle(sprintf("Blog performance within 30 Days of Publication", name))+ #,subtitle = "Unique User Views" ) +
	geom_bar(aes(fill = author_categories),stat="identity",width=.2, position = "dodge")+coord_flip()+my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) +
	scale_y_continuous(expand = c(0, .3))

### Generate time period dates ###
ninty_days= subset(df_final , days_aft_pub <= 150)
ninty_days$days_aft_pub= ifelse(ninty_days$days_aft_pub < 0, 0, ninty_days$days_aft_pub)
ninty_days =subset(ninty_days, type == "blog") # blogs only
ninty_days=aggregate(sessions ~ title+author_categories, ninty_days, sum)
ninty_days$title<-factor(ninty_days$title,levels=ninty_days$title[order(ninty_days$sessions)])

ggplot(data=ninty_days, aes(x=title,y=sessions,colour=author_categories) ) +
	ggtitle(sprintf("Blog performance within 90 Days of Publication", name))+ #,subtitle = "Unique User Views" ) +
	geom_bar(aes(fill = author_categories),stat="identity",width=.2, position = "dodge")+coord_flip()+my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) +
	scale_y_continuous(expand = c(0, .3))


# ninty_days=aggregate(sessions ~ title + days_aft_pub, ninty_days, sum)
# plot_30=ninty_days %>% ggplot(aes(x=days_aft_pub,y=sessions,group=title,colour=title))+geom_line()+
# 	theme(axis.text.x=element_text(angle=90,hjust = 1),legend.position="none")+my_theme()+
# 	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank()) 
# library(ggrepel)
# plot_30 + geom_label_repel(data = subset(ninty_days, 
# 												    days_aft_pub == max(days_aft_pub)),
# 	aes(label=title), size=2)
#+ theme(legend.position = "None")   # label
```

\pagebreak

This section examines time spent on reading an article relative to the number of words of text in the article.  Below are the 10 best and worst performing articles.  Multimedia (e.g. Podcasts) are ignored. This measure is designed to give you a rough idea of the types of articles people are likely to read through. 

**Note:** This measure has some methodological issues related to sample size that need to be addressed and thus should be treated solely as an illustration.  

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
#Time per Article
Audience_Captivation =subset(df_final, type != "events" & type != "multimedia") # Remove Events and Multimedia
Audience_Captivation <- aggregate(avg_MinPerWord ~ title+author_categories, Audience_Captivation, mean)

# Happy
Happy_audience=filter(Audience_Captivation, row_number(-avg_MinPerWord) <= 10)
Happy_audience <- Happy_audience %>% arrange(avg_MinPerWord)
Happy_audience$title<-factor(Happy_audience$title,levels=Happy_audience$title[order(Happy_audience$avg_MinPerWord)])
ggplot(data=Happy_audience, aes(x=title, y=avg_MinPerWord, fill=author_categories) ) +
	ggtitle(sprintf("10 Best Audience Attrition", name),subtitle = "Time Spent per Word in Aticle Text" ) +
	geom_bar(stat="identity", width=0.5)+ coord_flip() + my_theme()+ 
	theme(legend.position="bottom",  legend.box = "horizontal")+theme(legend.title=element_blank()) 
```

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=4, fig.width=7}
# Sad Audience
sad_audience<-filter(Audience_Captivation, row_number(avg_MinPerWord) <= 10)
sad_audience <- sad_audience %>% arrange(avg_MinPerWord)
sad_audience$title<-factor(sad_audience$title,levels=sad_audience$title[order(sad_audience$avg_MinPerWord)])
ggplot(data=sad_audience, aes(x=title, y=avg_MinPerWord, fill=author_categories))+
	ggtitle(sprintf("10 Worst Audience Attrition", name),subtitle="Time Spent per Word in Aticle Text")+
	geom_bar(stat="identity", width=0.5)+ coord_flip() + my_theme()+
	theme(legend.position="bottom", legend.box = "horizontal")+theme(legend.title=element_blank())

```

More to come on this...
